Outline paper - Multiple imputation for statistical disclosure control: Creating synthetic datasets with *mice*

### 2021-09-30 mice_synthesizing/paper.Rmd
Add some figures for result section.

>>>>

# Variable plots

```{r}
## Merely illustrative, single dataset, plot of age
synthetic_samples[[1]] %>% 
  complete(action = "long", include = TRUE) %>%
  mutate(Synthetic = ifelse(.imp == 0, "Real data", "Synthetic data")) %>%
  ggplot(mapping = aes(x = age, y = ..density.., fill = Synthetic)) +
  geom_histogram(position = "dodge") +
  scale_fill_brewer(palette = "Paired") +
  theme_classic()

## Merely illustrative, single dataset, plot of gen

synthetic_samples[[234]] %>%
  complete(action = "long", include = TRUE) %>% 
  mutate(Synthetic = ifelse(.imp == 0, "Real data", "Synthetic data")) %>%
  ggplot(mapping = aes(x = gen, fill = Synthetic, group = Synthetic)) +
  geom_bar(aes(y = ..prop..), position = "dodge2") +
  scale_fill_brewer(palette = "Paired") +
  theme_classic()

## Merely illustrative, single dataset, plot of bmi by region
synthetic_samples[[678]] %>%
  complete(action = "long", include = TRUE) %>%
  mutate(Synthetic = ifelse(.imp == 0, "Real data", "Synthetic data")) %>%
  ggplot(mapping = aes(x = reg, y = bmi, fill = Synthetic)) +
  geom_boxplot() +
  scale_fill_brewer(palette = "Paired") +
  theme_classic()
```

# Parameter plots

```{r}
# Univariate -- sampling distribution of the mean of age
synthetic_samples %>%
  map_dfr(function(x) {
    x %>%
      complete(action = "long", include = TRUE) %>%
      mutate(Synthetic = ifelse(.imp == 0, "Real data", "Synthetic data")) %>%
      group_by(Synthetic) %>%
      dplyr::summarize(`Mean age` = mean(age))
}) %>%
  ggplot(mapping = aes(x = `Mean age`, y = ..density.., fill = Synthetic)) +
  geom_histogram(position = "dodge") +
  scale_fill_brewer(palette = "Paired") +
  theme_classic()

# Univariate -- sampling distribution of the proportion of cases in 
# every gen category
synthetic_samples %>%
  map_dfr(function(x) {
    x %>%
      complete(action = "long", include = TRUE) %>% 
      mutate(Synthetic = ifelse(.imp == 0, "Real data", "Synthetic data")) %>%
      group_by(Synthetic, gen) %>%
      dplyr::summarize(number = n(), .groups = "drop") %>%
      group_by(Synthetic) %>%
      mutate(prop = number / sum(number))
  }) %>%
  ggplot(aes(x = gen, y = prop, fill = Synthetic)) +
  geom_boxplot() +
  scale_fill_brewer(palette = "Paired") +
  theme_classic()

bind_rows(`Real data`      = select(true_age, 
                                    Variable = term, 
                                    Estimate = estimate),
          `Synthetic data` = select(synthetic_age, 
                                    Variable = term, 
                                    Estimate = estimate),
          .id = "Synthetic") %>%
  ggplot(aes(x = Estimate, fill = Synthetic)) +
  geom_density(alpha = 0.8) +
  scale_fill_brewer(palette = "Set1") +
  theme_classic() +
  facet_wrap(~Variable, scales = "free")

bind_rows(`Real data`      = select(true_wgt, 
                                    Variable = term, 
                                    Estimate = estimate),
          `Synthetic data` = select(synthetic_wgt, 
                                    Variable = term, 
                                    Estimate = estimate),
          .id = "Synthetic") %>%
  ggplot(aes(x = Estimate, fill = Synthetic)) +
  geom_density(alpha = 0.8) +
  scale_fill_brewer(palette = "Set1") +
  theme_classic() +
  facet_wrap(~Variable, scales = "free")

bind_rows(`Real data`      = select(true_gen,
                                    Variable = term, 
                                    Estimate = estimate),
          `Synthetic data` = select(synthetic_gen,
                                    Variable = term,
                                    Estimate = estimate),
          .id = "Synthetic") %>%
  ggplot(aes(x = Estimate, fill = Synthetic)) +
  geom_density(alpha = 0.8) +
  scale_fill_brewer(palette = "Set1") +
  theme_classic() +
  facet_wrap(~Variable, nrow = 4, scales = "free") +
  theme(legend.position = "right")
```
